Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-16 edubots_surveys.Rnw
Eliminated by agreement, suggested by @oliatsi

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
#ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Gender$source<-rep("survey1")
freqInteraction.Gender$source<-rep("survey2")
freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
freqbinded.Gender[as.character(freqbinded.Gender$Gender)!="No", ] -> df1
ggplot(df1, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/gender.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
#ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Age$source<-rep("survey1")
freqInteraction.Age$source<-rep("survey2")
freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
freqbinded.Age$source <- factor(freqbinded.Age$source) 
freqbinded.Age[as.character(freqbinded.Age$Age)!="No", ] -> df1
ggplot(df1, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/age.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
#ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Sector$source<-rep("survey1")
freqInteraction.Sector$source<-rep("survey2")
freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/sector.pdf}
    \end{minipage}
    \vspace{0.5mm}
    \begin{minipage}[t]{0.38\textwidth}
        \centering
<<experience, echo=FALSE, fig.width=4.5, fig.height=3.475>>=
#ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Experience$source<-rep("survey1")
freqInteraction.Experience$source<-rep("survey2")
freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
freqbinded.Experience[as.character(freqbinded.Experience$Experience)!="No", ] -> df1
ggplot(df1, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@        
%       \includegraphics[width=\textwidth]{figures/experience.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.52\textwidth}
        \centering
<<discipline,echo=FALSE, fig.width=8.2, fig.height=4.45>>=
#ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Discipline$source<-rep("survey1")
freqInteraction.Discipline$source<-rep("survey2")
freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/discipline.pdf}
    \end{minipage}
\end{center}
    \caption{Sample population description. The responses from two surveys were collected amount to 282 for the first survey (\textit{survey1} in red) and 205 for the second (\textit{survey2} in blue). Data are shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
\label{figure:teachers_population}
\end{figure}

% Olia suggests to delete this, as well as figure 1.
Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages. At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.

>>>>

% \begin{figure}[h!tbp]
% \begin{center}
%     \begin{minipage}[t]{0.3\textwidth}
%         \centering
% <<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
% #ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
% freq.Gender$source<-rep("survey1")
% freqInteraction.Gender$source<-rep("survey2")
% freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
% freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
% freqbinded.Gender[as.character(freqbinded.Gender$Gender)!="No", ] -> df1
% ggplot(df1, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
% @
% 
% %       \includegraphics[width=\textwidth]{figures/gender.pdf}
%     \end{minipage}
%     \begin{minipage}[t]{0.3\textwidth}
%         \centering
% <<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
% #ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
% freq.Age$source<-rep("survey1")
% freqInteraction.Age$source<-rep("survey2")
% freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
% freqbinded.Age$source <- factor(freqbinded.Age$source) 
% freqbinded.Age[as.character(freqbinded.Age$Age)!="No", ] -> df1
% ggplot(df1, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
% @
% 
% %       \includegraphics[width=\textwidth]{figures/age.pdf}
%     \end{minipage}
%     \begin{minipage}[t]{0.3\textwidth}
%         \centering
% <<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
% #ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
% freq.Sector$source<-rep("survey1")
% freqInteraction.Sector$source<-rep("survey2")
% freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
% freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
% ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
% @
% %       \includegraphics[width=\textwidth]{figures/sector.pdf}
%     \end{minipage}
%     \vspace{0.5mm}
%     \begin{minipage}[t]{0.38\textwidth}
%         \centering
% <<experience, echo=FALSE, fig.width=4.5, fig.height=3.475>>=
% #ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
% freq.Experience$source<-rep("survey1")
% freqInteraction.Experience$source<-rep("survey2")
% freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
% freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
% freqbinded.Experience[as.character(freqbinded.Experience$Experience)!="No", ] -> df1
% ggplot(df1, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
% @        
% %       \includegraphics[width=\textwidth]{figures/experience.pdf}
%     \end{minipage}
%     \begin{minipage}[t]{0.52\textwidth}
%         \centering
% <<discipline,echo=FALSE, fig.width=8.2, fig.height=4.45>>=
% #ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
% freq.Discipline$source<-rep("survey1")
% freqInteraction.Discipline$source<-rep("survey2")
% freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
% freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
% freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
% ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
% @
% 
% %       \includegraphics[width=\textwidth]{figures/discipline.pdf}
%     \end{minipage}
% \end{center}
%     \caption{Sample population description. The responses from two surveys were collected amount to 282 for the first survey (\textit{survey1} in red) and 205 for the second (\textit{survey2} in blue). Data are shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
% \label{figure:teachers_population}
% \end{figure}

% % Olia suggests to delete this, as well as figure 1.
% Figure \ref{figure:teachers_population} shows the distribution of age and experience are quite similar. %, and as a matter of fact,
% Additionally, as a matter of fact, as Figure \ref{figure:age.vs.exp} shows, age and experience are correlated strongly, with experience being roughly 20-30 years less than age. 
% This might indicate that a differential analysis for age and experience will not yield significant differences, except maybe in the 6-15 years experience group, which is spread over all ages. At any rate, experience seems to be the dominating factor here and we'll use experience only unless we detect some significant difference by age.
